Action alternatives & confidence factor

### 2023-08-03 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update action alternatives

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, Event, `Confidence Factor`) %>% 
  filter(
    ID %in% c(101:126, 201:228),
    !ID %in% c(204, 226),
    Event %in% c("chatting")) %>%
  janitor::clean_names()

@@

@@

# sjt cm
describeBy(main$sjt, main$id)
plot_confi <- boxplot(sjt ~ id, data = main)

@@

# action alternatives - non disruptive alternatives  
describeBy(main$nd, main$id)
plot_action_quality <- boxplot(nd ~ id, data = main)

@@

# confidence factor x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

@@

### action alternatives non-disruptive
# t-test for expertise differences
t.test(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)
```

@@

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_confi_nd_corr <- corr.test(main$confidence_factor, 
                                main$nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_nd_corr,
      short = F)

@@

# novices: correlation between count and non-disruptive alternatives
nov_count_nd_corr <- cor.test(corr.nov$count,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives
exp_count_nd_corr <- cor.test(corr.exp$count,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_count_nd_corr <- corr.test(main$count, 
                                main$nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)

@@

# novices: correlation between sjt and count
nov_sjt_count_corr <- cor.test(corr.nov$sjt,
                              corr.nov$count, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_sjt_count_corr, 
      short = F)

# experts: correlation between sjt and count
exp_sjt_count_corr <- cor.test(corr.exp$sjt,
                              corr.exp$count, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_sjt_count_corr,
      short = F)

# full sample: correlation between sjt and count
full_sjt_count_corr <- corr.test(main$sjt, 
                                 main$count, 
                                 method=c("pearson"), 
                                 adjust="holm")
print(full_sjt_count_corr, 
      short = F)

# novices: correlation between sjt and non-disruptive alternatives
nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_sjt_nd_corr, 
      short = F)

# experts: correlation between sjt and non-disruptive alternatives
exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_sjt_nd_corr,
      short = F)

# full sample: correlation between sjt and non-disruptive alternatives
full_sjt_nd_corr <- corr.test(main$sjt,
                              main$nd,
                              method=c("pearson"),
                              adjust="holm")
print(full_sjt_nd_corr,
      short = F)

>>>>

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, event, confidence_factor) %>% 
  filter(!ID %in% c(141,
                    142,
                    204,
                    226), # filter relevant rows
         event %in% c("chatting")) %>%
  janitor::clean_names()

@@

# creating new column with total reactions
main_novice <- main %>%
  filter(id %in% c("Novice")) %>% 
  mutate(
    # reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
    # percent_reaction = round((reaction_sum/sum_participants),digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# creating new column with total reactions
main_expert <- main %>%
  filter(id %in% c("Expert")) %>% 
  mutate(
    # reaction_sum = sum(reaction),
         nd_sum = sum(nd),
         sum_participants = sum(n()),
    # percent_reaction = round((reaction_sum/sum_participants), digits = 2),
         percent_nd = round((nd/count),
                            digits = 2)
         )

# merge novice & expert data frame
main <- rbind(main_expert, main_novice)

@@

# # sjt cm
# describeBy(main$sjt, main$id)
# plot_confi <- boxplot(sjt ~ id, data = main)

@@

# action alternatives - non disruptive alternatives  
describeBy(main$percent_nd, main$id)
plot_action_quality <- boxplot(percent_nd ~ id, data = main)

@@

# confidence factor x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(percent_nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = percent_nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

@@

### action alternatives non-disruptive
# t-test for expertise differences
t.test(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$percent_nd[main$id == "Expert"],
       y = main$percent_nd[main$id == "Novice"],
       na.rm = TRUE)

@@

# novices: correlation between confidence factor and non-disruptive alternatives
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_confi_nd_corr <- corr.test(main$confidence_factor, 
                                main$percent_nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_nd_corr,
      short = F)

@@

# novices: correlation between count and non-disruptive alternatives
nov_count_nd_corr <- cor.test(corr.nov$count,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_count_nd_corr, 
      short = F)

# experts: correlation between count and non-disruptive alternatives
exp_count_nd_corr <- cor.test(corr.exp$count,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_count_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives
full_count_nd_corr <- corr.test(main$count, 
                                main$percent_nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)

@@

# # novices: correlation between sjt and count
# nov_sjt_count_corr <- cor.test(corr.nov$sjt,
#                               corr.nov$count, 
#                               method=c("pearson"),
#                               adjust="holm")
# print(nov_sjt_count_corr, 
#       short = F)
# 
# # experts: correlation between sjt and count
# exp_sjt_count_corr <- cor.test(corr.exp$sjt,
#                               corr.exp$count, 
#                               method=c("pearson"),
#                               adjust="holm")
# print(exp_sjt_count_corr,
#       short = F)
# 
# # full sample: correlation between sjt and count
# full_sjt_count_corr <- corr.test(main$sjt, 
#                                  main$count, 
#                                  method=c("pearson"), 
#                                  adjust="holm")
# print(full_sjt_count_corr, 
#       short = F)
# 
# 
# ###################################################
# 
# # novices: correlation between sjt and non-disruptive alternatives
# nov_sjt_nd_corr <- cor.test(corr.nov$sjt,
#                               corr.nov$nd, 
#                               method=c("pearson"),
#                               adjust="holm")
# print(nov_sjt_nd_corr, 
#       short = F)
# 
# # experts: correlation between sjt and non-disruptive alternatives
# exp_sjt_nd_corr <- cor.test(corr.exp$sjt,
#                               corr.exp$nd, 
#                               method=c("pearson"),
#                               adjust="holm")
# print(exp_sjt_nd_corr,
#       short = F)
# 
# 
# # full sample: correlation between sjt and non-disruptive alternatives
# full_sjt_nd_corr <- corr.test(main$sjt,
#                               main$nd,
#                               method=c("pearson"),
#                               adjust="holm")
# print(full_sjt_nd_corr,
#       short = F)
